Constraints on Cosmic-Ray Particle Populations, Magnetic Fields, and Dark Matter from VHE Gamma-Ray Observations of the Coma Cluster of Galaxies with VERITAS

### 2011-09-01 ms.tex
Citations updated

The ICM is a hot, $T\sim 10^{8}$ K, plasma emitting thermal bremsstrahlung radiation in the soft X-rays regime \citep[see, e.g.,][]{article:Petrosian:2001}. This plasma has been heated to these temperatures primarily through collisionless structure-formation shocks that form as a result of the hierarchical merging and accretion processes. Such shocks and turbulence in the ICM gas and intra-cluster magnetic fields also
provide a means to efficiently accelerate particles \citep[see, e.g.,][]{article:ColafrancescoBlasi:1998, article:Ryu_etal:2003}. Many clusters do indeed feature mega-parsec scale halos of non-thermal radio emission, indicative of a population of relativistic electrons and positrons (leptons) and magnetic fields permeating the ICM \citep{article:Cassano_etal:2010}. Recent observations of possible non-thermal emission from clusters in the the extreme ultraviolet \citep[EUV; ][]{article:SarazinLieu:1998} and hard X-rays
\citep{article:RephaeliGruber:2002, article:Fusco-Femiano_etal:2004, article:Eckert_etal:2007} may provide further indications of relativistic particle populations in clusters, although the interpretation of these
observations as non-thermal diffuse emission have been disputed on the basis of more sensitive observations \citep[see, e.g.,][]{2009ApJ...690..367A, 2010ApJ...725.1688A, article:Wik_etal:2009}.

>>>>

The ICM is a hot, $T\sim 10^{8}$ K, plasma emitting thermal bremsstrahlung radiation in the soft X-rays regime \citep[see, e.g.,][]{article:Petrosian:2001}. This plasma has been heated to these temperatures primarily through collisionless structure-formation shocks that form as a result of the hierarchical merging and accretion processes. Such shocks and turbulence in the ICM gas and intra-cluster magnetic fields also
provide a means to efficiently accelerate particles \citep[see, e.g.,][]{article:ColafrancescoBlasi:1998, article:Ryu_etal:2003}. Many clusters do indeed feature mega-parsec scale halos of non-thermal radio emission, indicative of a population of relativistic electrons and positrons (leptons) and magnetic fields permeating the ICM \citep{article:Cassano_etal:2010}. Recent observations of possible non-thermal emission from clusters in the the extreme ultraviolet \citep[EUV; ][]{article:SarazinLieu:1998} and hard X-rays
\citep{article:RephaeliGruber:2002, article:Fusco-Femiano_etal:2004, article:Eckert_etal:2007} may provide further indications of relativistic particle populations in clusters, although the interpretation of these
observations as non-thermal diffuse emission have been disputed on the basis of more sensitive observations \citep[see, e.g.,][]{article:Ajello_etal:2009, article:Ajello_etal:2010, article:Wik_etal:2009}.
